Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh \emph{hp}-FEM

### 2011-02-19 results.tex
Results section improved

The Debye length $\lambda_D$ is the screening length in the electrolyte
solutions. Its numerical value shows the
thickness of the layer in the vicinity of the boundaries $\partial\Omega_1$ 
and $\partial\Omega_2$  where $c \neq 1$.
In all the previous simulations, the Debye screening length was determined by  the constants in
Table~\ref{Table:used-constants} and Eq.~\ref{eq:debye}: $\lambda_D=XXX$. It is known that computation gets increasingly
difficult when reducing the value of $\lambda_D$.
It was our interest to see how small screening lengths can Hermes HP\_ANISO automatic
adaptivity handle. The parameter $\varepsilon$ was varied as follows:
$$\varepsilon_n=\varepsilon\times 0.5^n,$$ where $\varepsilon$ is taken from Table~\ref{Table:used-constants}. The simulations were run for each $\varepsilon_n$ and corresponding $\lambda_D$ value
and maximum number of degrees of freedom and cumulative CPU time were recorded.
The simulation time $t$ for each $\lambda_D$ was chosen to be $\tau$ --- the
characteristic time scale --- and each simulation
was divided equally into fifteen time steps. No PID controller was used.

>>>>

The Debye length $\lambda_D$ is the screening length in the electrolyte
solutions. Its numerical value shows the
thickness of the layer in the vicinity of the boundaries $\partial\Omega_1$ 
and $\partial\Omega_2$  where $c \neq 1$.
In all the previous simulations, the Debye screening length was determined by  the constants in
Table~\ref{Table:used-constants} and Eq.~\ref{eq:debye}: $\lambda_D=XXX$. It is known that computation gets increasingly
difficult when reducing the value of $\lambda_D$.
It was our interest to see how small screening lengths can Hermes HP\_ANISO automatic
adaptivity handle. The parameter $\varepsilon$ was varied as follows:
$$\varepsilon_n=\varepsilon\times 0.5^n,$$ where $\varepsilon$ is taken from Table~\ref{Table:used-constants}. The simulations were run for each $\varepsilon_n$ and corresponding $\lambda_D$ value
and maximum number of degrees of freedom and cumulative CPU time were recorded.
The simulation time $t$ for each $\lambda_D$ was chosen to be $\tau$ --- the
characteristic time scale --- and each simulation
was divided equally into fifteen time steps. No PID controller was used.
Fig.~XXX shows the maximum number of degrees of freedom during calculation
as a function of the Debye length and Fig.~XXX shows cumulative CPU time as a function
of the Debye length. The simulations up to XXX m screening length were carried out on
the initial coarse mesh. However, from $\lambda_D > XXX$ the finer initial mesh had to
be used so the existence of the large gradients of the
physical fields $c$ and $\varphi$ near the boundaries could be captured in the first place.
The fine mesh allowed simulations with the Debye length down to $XXX$~m. The calculated
$c$ and $\varphi$ at $t=\tau$ for $\lambda_D=XXX$ are shown in Fig.~XXX.
It appears that when using even finer initial mesh and higher initial polynomial degrees, even
smaller Debye lengths could be used when necessary.
